\documentclass[a4paper,10pt]{article}
\usepackage[top=0.75in, bottom=0.75in, left=0.50in, right=0.75in]{geometry}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[colorlinks=true, urlcolor=blue, urlbordercolor={0 1 1}]{hyperref}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\lsep}{-0.5cm}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage} \hspace{0.2cm}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
\multirow{3}{*}{\huge\textsc{\textbf{Ashish Tiwari}}}	& \textbf{Email:} \href{mailto:ashishtiwari11@outlook.com}{ashishtiwari11@outlook.com}				\\
							& \textbf{Website:} \href{https://github.com/danny1105?tab=repositories}{github.com/danny1105}	\\
							& \textbf{Phone:} +91 998 749 3591
\end{tabular*}

\resheading{\textbf{ACADEMIC DETAILS}}\\[\lsep]
\\ \\
\indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}cccc}
\hline
\textbf{Year}	&	\textbf{Degree / Certificate}		&	\textbf{University / School}	   &	\textbf{CPI / \%}	\\
\hline
2016	&	B. Tech (Computer Science and Engineering)	&	BBDNITM, Lucknow&	   			        64.40 \%		\\[0.15cm]
%2012	&	Class XII (ISC)					     		&	Raja Rammohan Roy Academy, Dehradun&	84.40 \%		\\[0.15cm]
%2010	&	Class X (ICSE)								&	Raja Rammohan Roy Academy, Dehradun&	84.30 \%		\\
\hline
\end{tabular*}
\\ \\
%\indent \resheading{\textbf{FIELDS OF INTEREST}}\\[\lsep]
%\\ \\
%\indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lll}
%  Artificial Intelligence & Distributed Computing\\
%\end{tabular*}
%\\
%\\\indent \resheading{\textbf{Work Experience Aug 2016 Till Present}}\\[\lsep]
\indent \resheading{\textbf{Current Employer: Tata Consultancy Services} \hfill   \small{\textit{Aug'16 - Present}}}\\[\lsep]
\\ \\
\indent\small{\textbf{Application:Large Cash Reporting}	\hfill	\small{\textit{(Mar'17 - Aug'17)}}
\begin{itemize}
 \item Large Cash Reporting is an application, which tracks cash transactions, by both account number and Social Security/Tax Id when the net aggregate of an individual exceeds 10,000 dollars per day.
 \item It will send currency transaction report (CTR) file to IRS in compliance with legal requirements.
\end{itemize}

\indent\small{\textbf{Application:Abndoned Property and Tracker}	\hfill	\small{\textit{(Sep'17 - Present)}}
\begin{itemize}
 \item ABP application manages the Escheatment of unclaimed Assets (Accounts and Instruments) to respective State based on the specific rules set by the Government. I am managing the Regulatory and Compliance change requests from States and implemented within the stipulated release timelines.
 \item Financial transaction (Closeouts and Fees) initiation and balancing for fund disbursements was the major area where the changes were requested by Business/State.
\end{itemize}

\resheading{TECHNICAL SKILLS} 
    \begin{itemize}
\item \textbf{Languages:\space} C ,\space C++,\space Python, \space Java, \space Cobol
\item \textbf{Tools:} Eclipse,\space Django\space, Codeblocks\space
\item \textbf{Version Control System:} Git and Changeman
\item \textbf{Platforms:} Linux and Windows
    \end{itemize}
    
    
\resheading{PROJECTS}
\begin{itemize}
  \item\indent\small{\textbf{Instant Messenger}	\hfill	\small{\textit{(July'18 - Present)}}
  \end{itemize}
  
It's a simple instant messaging system developed using intermediate JAVA concepts. It is based on client-server architecture.
    
\resheading{POSITIONS OF RESPONSIBILITY}
\\ \\
\indent\small{\textbf{Associate General Secretary of Computer Club (BBDNITM)}}	\hfill	\small{\textit{(Aug'15 - May'16)}}
\begin{itemize}
 \item Organized many coding contest and hacking workshops over my tenure.
 \item Ambassador of E-Cell IIT-Bombay.
 \item Ambassodor of Hackerrank.
\end{itemize}


\indent \resheading{\textbf{IMPORTANT COURSES UNDERTAKEN}}\\[\lsep]
\\ \\
\indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lll}
Design and Analysis of Algorithms &  Object Oriented Programming & Compiler Design \\
Database Management Systems
\end{tabular*}
\indent \resheading{\textbf{EXTRA CURRICULAR ACHIEVEMENTS}}\\[\lsep]
\\
\begin{itemize}
 \item Participated in TCS Codevita and my team was in the top 2000.
 \item Conducted Ethical Hacking Workshops in my college. 
\end{itemize}

\end{document}